Clean data

### 2020-01-14 analysis/02_clean-data.Rmd
Add other factor levels for summary table

```

@@

```{r save-clean-data}
write_csv(data, here("data", "derived_data", "final_data.csv"))
```

>>>>

# Add other factor levels
data <- data %>% 
  mutate(
    Q2.2 = factor(Q2.2, labels = c("Always", "Sometimes", "Never"), ordered = TRUE),
    Q2.6 = factor(Q2.6, 
                  labels = c("$1-$49", "$50-$99", "$100-$499", "$500-$999", 
                             "$1000-$4,999", "$5000-$9,999", "$10,000+"),
                  ordered = TRUE),
    Q2.7_f = factor(Q2.7, ordered = TRUE),
    Q2.8_f = factor(Q2.8, ordered = TRUE),
    Q2.9 = factor(Q2.9, labels = c("Yes", "No"), ordered = TRUE),
    Q5.1 = factor(Q5.1, labels = c("Yes", "No"), ordered = TRUE),
    Q5.2_f = factor(Q5.2, ordered = TRUE),
    Q5.6_f = factor(Q5.6, ordered = TRUE),
    Q5.7 = factor(Q5.7, labels = c("Yes", "No"), ordered = TRUE),
    Q5.11_f = factor(Q5.11, ordered = TRUE),
    Q5.12 = factor(Q5.12, labels = c("Male", "Female", "Transgender", 
                                     "Prefer not to say", "Other"), 
                   ordered = TRUE),
    Q5.13 = factor(Q5.13, labels = c("Married", "Widowed", "Divorced", 
                                     "Separated", "Never married"), 
                   ordered = TRUE),
    Q5.14 = factor(Q5.14, 
                   labels = c("Less than high school", "High school graduate", 
                              "Some college", "2 year degree", "4 year degree", 
                              "Graduate or professional degree", "Doctorate"),
                   ordered = TRUE)
  )
```

@@

```{r save-clean-data}
write_rds(data, here("data", "derived_data", "final_data.rds"))
```
